Theoretical prediction of disrupted Min oscillation in flattened \emph{Escherichia coli}

### 2015-07-27 paper/response-to-referees.txt

  <David>

Minor points:

10. As the referee requested, we have clarified the caption of Figure
1, to include the fact that these reactions are for a Min system
model that is used in this work.

11. The referee suggests that we should consistently write $\mu m^2$
over $\mu^2$ for square microns.  We have made this change to the plot
that used $\mu^2$.

### 2015-07-27 paper/plos.tex
fix a couple of very easy referee suggestions

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author Summary}
  When an E. Coli cell divides it must split into two relatively equal
  volumes in order to survive.  One mechanism that aids in this
  process is a system of proteins that oscillate between cell ends and
  help the original cell divide along its center.  A recent experiment
  found that by drastically deforming these cells this oscillation can
  be disrupted.  We examine these oscillations in similarly deformed
  cells computationally, using two widely used simulation models, and
  find good agreement using one of them.  The other model fails in a
  manner far more dramatic than has been previously observed.
  Furthermore, we find that the effect observed experimentally in
  asymmetric and flattened cells is primarily a result of the
  flattening and lateral expansion, not the asymmetry.

@@

However Fig.~\ref{randst-plot-ave} leaves unclear the importance of
the flattening and accompanying lateral expansion of the cell versus
cell shape irregularity and asymmetry in the temporal regularity of
the oscillations.  Although in the movies the stadiums appear to
display, on average over long time scales, a somewhat more regular
oscillation than appears in the irregular shapes \emph{A} and
\emph{B}, the limited time range of the arrow plots (350 seconds) is
inadequate to make this comparison.  We therefore return to the
correlation function between the number of proteins in a segment at
the top of the cell and the number of proteins in a segment at the
bottom of the cell.  \fixme{this is where Ill need to add the volumes} Fig.~\ref{fig:corr-B} shows this plot for shape
\emph{B} and stadium \emph{B}.  Here we plot correlations of
correlation times up to 500 seconds, a biologically relevant
timescale.  E. Coli cell doubling times vary widely depending on
environmental conditions, but will often be between 20 minutes to 100
minutes~\cite{pierucci1972chromosome}, while fluorescent microscopy
experiments have shown that the FtsZ ring builds itself with a half
life of roughly 30 seconds~\cite{stricker2002rapid}.

>>>>

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author Summary}
  When an E. coli cell divides it must split into two relatively equal
  volumes in order to survive.  One mechanism that aids in this
  process is a system of proteins that oscillate between cell ends and
  help the original cell divide along its center.  A recent experiment
  found that by drastically deforming these cells this oscillation can
  be disrupted.  We examine these oscillations in similarly deformed
  cells computationally, using two widely used simulation models, and
  find good agreement using one of them.  The other model fails in a
  manner far more dramatic than has been previously observed.
  Furthermore, we find that the effect observed experimentally in
  asymmetric and flattened cells is primarily a result of the
  flattening and lateral expansion, not the asymmetry.

@@

However Fig.~\ref{randst-plot-ave} leaves unclear the importance of
the flattening and accompanying lateral expansion of the cell versus
cell shape irregularity and asymmetry in the temporal regularity of
the oscillations.  Although in the movies the stadiums appear to
display, on average over long time scales, a somewhat more regular
oscillation than appears in the irregular shapes \emph{A} and
\emph{B}, the limited time range of the arrow plots (350 seconds) is
inadequate to make this comparison.  We therefore return to the
correlation function between the number of proteins in a segment at
the top of the cell and the number of proteins in a segment at the
bottom of the cell.  \fixme{this is where Ill need to add the volumes} Fig.~\ref{fig:corr-B} shows this plot for shape
\emph{B} and stadium \emph{B}.  Here we plot correlations of
correlation times up to 500 seconds, a biologically relevant
timescale.  E. coli cell doubling times vary widely depending on
environmental conditions, but will often be between 20 minutes to 100
minutes~\cite{pierucci1972chromosome}, while fluorescent microscopy
experiments have shown that the FtsZ ring builds itself with a half
life of roughly 30 seconds~\cite{stricker2002rapid}.
